MCC Models

### 2020-09-22 papers/full_paper/Supplementary_information.Rmd
fix forward sampling description

Here we report details on the model comparisons. Model fit was assessed based on marginal log-likelihoods of the data under each model. To compute the log-likelihood for models including a noise parameter, we used forward sampling on four independent chains to collect 5000 samples from the prior distribution of the noise parameter, calculated the log-likelihood for each sample and then averaged over the resulting distribution.

>>>>

Here we report details on the model comparisons. Model fit was assessed based on marginal log-likelihoods of the data under each model. To compute the log-likelihood for models including a noise parameter, we used forward sampling to collect 20,000 samples from the prior distribution of the noise parameter, calculated the log-likelihood for each sample and then averaged over the resulting distribution.
